\documentclass{article}

\usepackage{amsmath, amssymb}

\usepackage[a4paper]{geometry}
\usepackage{libertine}
\usepackage{libertinust1math}
\usepackage[T1]{fontenc}

\title{Game Project Proposal \\ \LARGE Golf Time}
\author{Chase Allen \and Isaac Boaz \and Jacob Jensen}

\begin{document}
\maketitle

\section*{Overview}
Golf Time will be a 3D golf game that allows the player to freeze time in
mid-air to adjust the trajectory of the ball. Level progression will include a
tutorial level that introduces basic game mechanics (camera, hitting ball),
followed by the introduction of time freezing mechanics.

The ability to modify the ball's trajectory mid-air will allow for an
interesting take on golf, and introduces a higher skill ceiling for dedicated
players. Enemies will be introduced in later levels which may hinder or otherwise prevent
the player from reaching the hole.

\subsection*{Potential Progression Systems}
\begin{itemize}
    \setlength{\itemsep}{0.2em}
    \item Coins dispersed around levels with a `store' to purchase upgrades on
    \item Items hidden around levels that grant new abilities
    \item `XP' system based on performance in levels
\end{itemize}

\subsection*{Potential Powerups}
\begin{description}
    \item[Better Time Freeze] Depending on exact implementation, the game may
          either \emph{slow down} time, or completely freeze it. Either the duration
          that the player can freeze time for, or the slowdown factor would be
          upgradable with this item.
    \item[Longer Indicator] In many games with balls, a line is drawn indicating where the
          ball would go if hit at that moment. This power-up would increase the length
          of that line, allowing for more precise shots.
    \item[More Power] This power-up would increase the maximum power that the
          player can hit the ball with.
    \item[Auto Shot] This power-up would automatically hit the ball at an optimal
          angle and power, removing the need for the player to hit the ball.
\end{description}

\section*{Sales Pitch}
Like golf? Probably not! It takes too long, right? But what if you could control
time -- \emph{while} golfing!? Need to adjust your shot in mid-air? In Golf
Time, you can do all of these things!
With challenging levels, in-depth progression, and even enemies, you'll have a
lot more than just where to hit the ball to think about. Become better than
Tiger Woods could ever be, or see your ball fall into the water despite your
magic powers. Golf Time is the game for you!
\end{document}